### 2007-01-14 Documentation/part1.tex
JK - Minor corrections in chapter 4

This approach also has one major disadvantage: There is \emph{no} such
thing as a global minimization algorithm or even an algorithm which guarantees
to find \emph{all} local minima of a function. In practice this means using 
 a local minimizer, one may end up in an unwanted local minimum and not in 
the investigated (possibly global) one or 
one may miss a local minimum which affects the results\footnote{NB -- 
Implementing a grid-based method which guarantees to find all local minima is
not straightforward either, to say the least.}. 
The only way out of this dilemma is to use some heuristic approach, \ie , 
one can use schemes which work
in most cases and announce their failure loudly. In order to use such a
heuristic some (analytical or numerical) knowledge on the topology of 
the fit manifold is necessary. With this knowledge it is possible
to obtain an approximate position for each local minimum 
and thus to start the local minimizer 
close enough to the investigated minimum.
 Fortunately, this can be done quite straightforward in most cases, since 
the structure of the neutrino oscillation formulas does not cause very 
complicated topologies of the fit manifolds. Especially the simulation of 
reactor experiments and conventional beams or superbeams is rather simple 
with purely numerical
approaches. Neutrino factories have, especially for small values of
$\theta_{13}$, a much more complicated topology. In this case, results
of the many analytical discussions of this issue can be used. This means
 that one can implicitly use the analytical knowledge to obtain 
better predictions for the location of a minimum. One can easily imagine 
that the used methods then also depend
on the region of the parameter space. In this manual, we mainly use
examples with a neutrino factory, since some of these complications
can be illustrated there. Note that the methods described here are neither
complete, nor will they work everywhere in the parameter space. It is
in any case up to the user to make sure that the results are what he/she
thinks.

Some more words of warning with respect to results obtained by projecting
the $\chi^2$:
The results obtained this way are always only a \emph{upper} bound on the
value of the projected $\chi^2$ function, \ie\ an undiscovered minimum 
decreases the value of the the projected $\chi^2$ function. If the value
of the $\chi^2$ function in the missed minimum is larger than the
previously found ones it will not influence the value of the projected 
value. 
Thus, one can only run the danger to obtain a too optimistic solution 
if one does not find the other local minima appearing 
below the chosen confidence level. With this approach and proper usage,
 it should not possible to produce a too pessimistic solution. 
However, if one is not careful enough to locate
all local minima, one can easily produce too optimistic solutions.
This danger can be summarized as follows:
\begin{equation}
\mathrm{Too \, pessimistic \, result} \, < \, \underbrace{\mathrm{Real \, result}}_{\mathrm{Located \, by \, careful \, usage}} \, \le \, \mathrm{GLoBES \, result} \,  < \,  \mathrm{Too \, optimisitic \, result} \nonumber
\end{equation}

\index{norm}{External information!priors} 
\index{norm}{External information!input errors} 
\index{norm}{External information!central values}
In many cases, the fit manifold is restricted by the knowledge 
from earlier experiments. For example, the knowledge on the solar 
parameters will in most cases be supplied by the solar neutrino experiments. 
If the external precision of a parameter is at the time of the 
measurement better than the one of the experiment itself, one usually will use
this external, better knowledge and impose a corresponding constraint
 on this parameter. This external knowledge may reduce the extension of the 
$n$-dimensional fit manifold in the respective direction. In the most 
extreme case, keeping all parameters but the measured one fixed 
in the analysis is equivalent to the assumption that all parameters 
are determined externally with infinitively high precisions. As this 
is a quite strong assumption, one should \emph{always} check the 
consequences of relaxing it and using realistic errors. Only if such
a test has demonstrated that the impact of the uncertainty on a 
given fit parameter is negligible, it can be assumed as fixed safely. 
 The inclusion of external input in \GLOBES\ is done by the use of 
Gau\ss ian {\em priors}: We assume that an external measurement has 
determined the measured parameter to be at the central value 
(which we call {\em central value}) with a $1 \sigma$ Gau\ss ian error 
(which we call {\em input error}). The explicit definition of these 
priors will be shown in the next section.

@@

\index{norm}{External information}
\index{norm}{External input| \see{External information}}
It is one of the strengths of the \GLOBES\ software to use external input 
in order to reduce the extension of the fit manifold with the knowledge 
from external
(earlier) measurements. The treatment of external input is done by the 
addition of Gau\ss ian so-called {\em priors} to the systematics-minimized 
$\chi^2$-function. For example, for the matter density, one obtains as the 
final projected $\chi^2_F$ after minimization over the matter density
scaling factor \index{norm}{Matter density!scaling factor} $\hat{\rho}$
\be
 \chi^2_F = \underset{\rho}{\mathrm{min}} \left( \chi^2(\hat{\rho}) +
 \frac{(\hat{\rho} - \hat{\rho}^0)^2}{\sigma_{\hat{\rho}}^2} \right).
\label{equ:priors}
\ee
This example is a very simple one, since in fact the
minimization is simultaneously performed over all priors and free oscillation 
parameters. In \equ{priors}, $\hat{\rho}^0$ is the {\em central value} of the 
prior, and $\sigma_{\hat{\rho}}$ the $1 \sigma$ absolute (half width) 
{\em input error}. Thus, it is assumed that an external measurement has 
determined the matter density with a precision (input error) 
$\sigma_{\hat{\rho}}$ at the central value $\hat{\rho}^0$. Usually, 
the central value is fixed at the best-fit value, and the input error 
to the $1 \sigma$ half width of the external measurement. For the matter 
density, $\hat{\rho}^0$  is usually set to $1.0$ corresponding to
the actual matter density profile such as given by the experiment
 definition file, and $\sigma_{\hat{\rho}}$ to the 
relative matter density uncertainty (\eg, $0.05$ for 5\% uncertainty).

@@

\index{norm}{External information!precision}
Eventually, a typical initialization of the external input with
$10\%$ external precisions for the solar 
parameters\footnote{In fact, accelerator-based long-baseline experiments 
are primarily sensitive to the product $\sin 2 \theta_{12} \cdot \sdm$, 
which means that these errors effectively add up to an error of this 
product of about $15\%$.}, 
and $5\%$ matter density uncertainties for all experiments looks like this:
\begin{quote}
{\tt
 glbDefineParams(input\_errors,theta12*0.1,0,0,0,sdm*0.1,0);\\  
 glbSetDensityParams(input\_errors,0.05,GLB\_ALL);\\
 glbSetCentralValues(true\_values);\\
 glbSetInputErrors(input\_errors);\\
}
\end{quote}
In this example, the central values are set to 
the true (simulated) values. Remember that initially the 
matter density scaling factors are 
all $1.0$, which means that they do not need to be adjusted for the
central values.

@@

The projection onto the $\stheta$- (or $\deltacp$-) axis is performed by fixing $\stheta$ (or $\deltacp$) and minimizing the $\chi^2$-function over all free fit parameters and the matter densities. We illustrate this method at the example of the projection of the two-dimensional manifold in the $\stheta$-$\deltacp$-plane onto the $\stheta$-axis in \figu{projex}. In this figure, the left-hand plot shows the correlation in the $\stheta$-$\deltacp$-plane computed with {\tt glbChiSys}. The right-hand plot illustrates the projection of this two-dimensional manifold onto the $\stheta$ axis by minimizing $\chi^2$ over $\deltacp$. In this simple example, the minimization is done along the vertical gray lines in the left hand plot. The obtained minima are located on the thick gray curve, which means the the right-hand plot represents the $\chi^2$-value along this curve. In fact, one can easily see that one obtains the correct projected $3 \sigma$ errors in this example (\cf, arrows). This figure illustrates the projection of a two-parameter correlation. In general, the full $n$-parameter correlation is treated similarly by the simultaneous (local) minimization over all free fit parameters.

@@

\index{norm}{Matter density!scaling factor}
The output of the minimizer in {\tt out} carries as many matter density scaling factors as there are experiments. Either
one (for the simulation of one experiment) or all (for the simulation of
all experiments) are different from $1.0$ if matter density uncertainties
are present, since each experiment may face other matter density conditions. 
The minimizers of individual experiments ``know'' which
experiment they are currently treating, which means that they only returned the
matter density scaling factor of the appropriate experiment.
For example, calculating {\tt glbChiTheta13} for the last experiment
number, the last density value will be returned.
This approach turns out to be extremely useful together with the
simulation of more than one experiment. One can, for instance, locate the
degeneracies of all individual experiments. In order to test if
these degeneracies are still present in the combination of all experiments (which has a very different topology), one can test the combination of experiments with the output {\tt out} from the individual experiments. In this case, even the correct matter density scaling factor
output is used.

@@

Since the number of different parameter vectors used by \GLOBES\ may be a bit confusing, we summarize the most common parameter sets used in the calculations:
\begin{description}
\item[The simulated/true values] are the values set in \GLB{SetRates}.
\item[The fit values] are the values in the first parameter {\tt in} of {\tt glbChiTheta13} (and the other minimization functions) which are {\em fixed} by definition (such as $\theta_{13}$ for {\tt glbChiTheta13}). 
\item[The starting point/educated guess for the minimizer] are the values in the first parameter {\tt in} of {\tt glbChiTheta13} (and the other minimization functions) which are {\em free} by definition (such as all but $\theta_{13}$ for {\tt glbChiTheta13}). 
\item[The minimization result] of the marginalization process are the values in the second parameter {\tt out} of {\tt glbChiTheta13} (and the other minimization functions) which are {\em free} by definition (such as all but $\theta_{13}$ for {\tt glbChiTheta13}). The other values in {\tt out} still correspond to the fit values. 
\item[The position of external priors,] \ie, the best-fit values of external input, is set by \GLB{SetCenralValues}.
\item[The magnitude of external errors,] \ie, the errors themselves of external input, is set by \GLB{SetInputErrors}.
\end{description}

@@

In general, one can show the measurement result in any $k$-dimensional hyperplane, where $k$ is smaller than the dimension of the parameter space $n$, and thus the dimension of the fit manifold. In this case, $k$ parameters are fixed and $n-k$ parameters are minimized over. One such example is the projection of the fit manifold onto the $\stheta$-$\deltacp$-plane, \ie, $k=2$ here. In this case, the two
parameters $\stheta$ and $\deltacp$ are kept fixed, and the others are
minimized over. 
The corresponding function is 
\index{norm}{Projection!$\theta_{13}$-$\deltacp$-plane}
\begin{function}
\GLBNS{ChiTheta13Delta}
{\tt double glbChiTheta13Delta(const glb\_params in, glb\_params out, int exp)} returns the projected $\chi^2$ onto the $\theta_{13}$-$\deltacp$-plane for the  experiment {\tt exp}. For the simulation of all initialized experiments,
use {\tt GLB\_ALL} for {\tt exp}. The values in {\tt in} are the guessed fit values for the minimizer (all parameters other than $\theta_{13}$ and $\deltacp$) and the fixed fit values of $\theta_{13}$ and $\deltacp$. The actually determined parameters at the minimum are returned in {\tt out}, where $\theta_{13}$ and $\deltacp$ are still at their fixed values. If {\tt out} is set to {\tt NULL}, this information will not be returned.
\end{function}
This function works analogously to the ones in the last section. They can, for example, be used to obtain a figure similar to \figu{projex}, left.
The example on page~\pageref{ex:corrproj} illustrates then the difference
between the projections of the ``eggs'' within the 
$\stheta$-$\deltacp$-plane onto the $\theta_{13}$-axis. 
Though the running time for one call of these functions is somewhat 
shorter than the one for the $\stheta$- or $\deltacp$-projections, one 
has to compute a two-dimensional array for such a figure (instead of a 
one-dimensional list). Therefore, the overall computational effort is 
much higher, \ie, in the order of hours. In many cases, it is therefore
convenient to run {\tt glbChiSys} first to obtain a picture of
the manifold and to adjust the parameter ranges. Then, one can run
{\tt glbChiTheta13Delta} for a complete evaluation of the problem
including correlations.

@@

In order to define arbitrary projections, we introduce the vector
\GLB{\_projection}, which is very similar to the
oscillation parameter vector {\tt glb\_params}.
Normally, the user does not need to access this type directly:
A set of function similar to the ones for {\tt glb\_params} is
provided. The purpose of {\tt glb\_projection} is to tell \GLOBES\ 
what parameters are fixed, and what are minimized over. Thus, in
comparison to {\tt glb\_params}, it does not take values for the
parameters, but flags \GLBC{GLB\_FIXED} or \GLBC{GLB\_FREE}.
For example, the projection onto the $\theta_{13}$-axis {\tt glbChiTheta13}
is nothing else than a special case of {\tt glbChiNP} with $\theta_{13}$
fixed and all the other parameters free. Similar to {\tt glb\_params},
the type {\tt glb\_projection} has to be allocated first, and freed
later. The access functions for {\tt glb\_projection} are summarized in \Tab~\ref{tab:defprojection}. Since the complete set is very similar to
the one for {\tt glb\_params}, we do not go into greater details here.

@@

User-defined priors are an advanced concept of \GLOBES\ 3.0 and higher. Therefore,
this section can be jumped over in a first reading of the manual.
They allow for arbitrary priors being added to the $\chi^2$ after the systematics
minimization and before the marginalization over the oscillation parameters (\cf, \equ{priors}).
Therefore, compared to user-defined systematics, they depend on the oscillation
parameters only, but not on the systematics parameters. Examples for applications
are non-Gaussian external input, the combination with externally simulated experiments, and the
constraint to certain parameter-subspaces (such as a specific octant).

@@

The prior function has to be any function using one parameter {\tt glb\_params} containing the fit values.
We show an example for a user-defined prior on page~\pageref{ex:userprior}. This prior
will simply be registered with
\begin{quote}
{\tt
 glbInit(argv[0]); \\
 glbRegisterPriorFunction(my\_prior,NULL,NULL,NULL);
}
\end{quote}
and replaces the standard prior of \GLOBES . It behaves exactly as the standard prior, but
the solar mixing angle is interpreted as $\sin^2 \theta_{12}$ instead of $\theta_{12}$. Therefore,
a Gaussian error is imposed on $\sin^2 \theta_{12}$ instead of $\theta_{12}$, and the central
values and input errors are interpreted in terms of $\sin^2 \theta_{12}$ as well. Note that
one does not need to know if the prior was called for one experiment only or all experiments,
since this information is implicitely given by the different density projection flags being set
accordingly.

>>>>

This approach also has one major disadvantage: There is \emph{no} such
thing as a global minimization algorithm or even an algorithm which guarantees
to find \emph{all} local minima of a function. In practice this means using 
 a local minimizer, one may end up in an unwanted local minimum and not in 
the investigated (possibly global) one or 
one may miss a local minimum which affects the results\footnote{NB -- 
Implementing a grid-based method which guarantees to find all local minima is
not straightforward either, to say the least.}. 
The only way out of this dilemma is to use some heuristic approach, \ie , 
one can use schemes which work
in most cases and announce their failure loudly. In order to use such a
heuristic some (analytical or numerical) knowledge on the topology of 
the fit manifold is necessary. With this knowledge it is possible
to obtain an approximate position for each local minimum 
and thus to start the local minimizer 
close enough to the investigated minimum.
 Fortunately, this can be done quite straightforwardly in most cases, since 
the structure of the neutrino oscillation formulas does not cause very 
complicated topologies of the fit manifolds. Especially the simulation of 
reactor experiments and conventional beams or superbeams is rather simple 
with purely numerical
approaches. Neutrino factories have, especially for small values of
$\theta_{13}$, a much more complicated topology. In this case, results
of the many analytical discussions of this issue can be used. This means
 that one can implicitly use the analytical knowledge to obtain 
better predictions for the location of a minimum. One can easily imagine 
that the used methods then also depend
on the region of the parameter space. In this manual, we mainly use
examples with a neutrino factory, since some of these complications
can be illustrated there. Note that the methods described here are neither
complete, nor will they work everywhere in the parameter space. It is
in any case up to the user to make sure that the results are what he/she
thinks.

Some more words of warning with respect to results obtained by projecting
the $\chi^2$:
The results obtained this way are always only an \emph{upper} bound on the
value of the projected $\chi^2$ function, \ie\ an undiscovered minimum 
decreases the value of the the projected $\chi^2$ function. If the value
of the $\chi^2$ function in the missed minimum is larger than the
previously found ones it will not influence the value of the projected 
value. 
Thus, one can only run the danger to obtain a too optimistic solution 
if one does not find the other local minima appearing 
below the chosen confidence level. With this approach and proper usage,
 it should not be possible to produce a too pessimistic solution. 
However, if one is not careful enough to locate
all local minima, one can easily produce too optimistic solutions.
This danger can be summarized as follows:
\begin{equation}
\mathrm{Too \, pessimistic \, result} \, < \, \underbrace{\mathrm{Real \, result}}_{\mathrm{Located \, by \, careful \, usage}} \, \le \, \mathrm{\GLOBES \, result} \,  < \,  \mathrm{Too \, optimisitic \, result} \nonumber
\end{equation}

\index{norm}{External information!priors} 
\index{norm}{External information!input errors} 
\index{norm}{External information!central values}
In many cases, the fit manifold is restricted by the knowledge 
from earlier experiments. For example, the knowledge on the solar 
parameters will in most cases be supplied by the solar neutrino experiments. 
If, at the time of the measurement, the external precision of a parameter is
better than the one of the considered experiment itself, one usually will use
this better, external knowledge and impose a corresponding constraint
 on this parameter. The external knowledge may reduce the extension of the 
$n$-dimensional fit manifold in the respective direction. In the most 
extreme case, keeping all parameters but the measured one fixed 
in the analysis is equivalent to the assumption that all parameters 
are determined externally with infinitively high precision. As this 
is quite a strong assumption, one should \emph{always} check the 
consequences of relaxing it and using realistic errors. Only if such
a test has demonstrated that the impact of the uncertainty on a 
given fit parameter is negligible, it can safely be assumed as fixed. 
 The inclusion of external input in \GLOBES\ is done by the use of 
Gau\ss ian {\em priors}: We assume that an external measurement has 
determined the measured parameter to be at the \emph{central value}
with a $1 \sigma$ Gau\ss ian error (which we call {\em input error}).
The explicit definition of these priors will be shown in the next section.

@@

\index{norm}{External information}
\index{norm}{External input| \see{External information}}
It is one of the strengths of the \GLOBES\ software to use external input 
in order to reduce the extension of the fit manifold with the knowledge 
from external
(earlier) measurements. The treatment of external input is done by the 
addition of Gau\ss ian so-called {\em priors} to the systematics-minimized 
$\chi^2$-function. For example, for the matter density, one obtains as the 
final projected $\chi^2_F$ after minimization over the matter density
scaling factor \index{norm}{Matter density!scaling factor} $\hat{\rho}$
\be
 \chi^2_F = \underset{\rho}{\mathrm{min}} \left( \chi^2(\hat{\rho}) +
 \frac{(\hat{\rho} - \hat{\rho}^0)^2}{\sigma_{\hat{\rho}}^2} \right).
\label{equ:priors}
\ee
This example is a very simple one, since in fact the
minimization is simultaneously performed over all priors and free oscillation 
parameters. In \equ{priors}, $\hat{\rho}^0$ is the {\em central value} of the 
prior, and $\sigma_{\hat{\rho}}$ the $1 \sigma$ absolute (half width) 
{\em input error}. Thus, it is assumed that an external measurement has 
determined the matter density with a precision (input error) 
$\sigma_{\hat{\rho}}$ at the central value $\hat{\rho}^0$. Usually, 
the central value is fixed at the best-fit value, and the input error 
is chosen as the $1 \sigma$ half width of the external measurement. For the matter 
density, $\hat{\rho}^0$  is usually set to $1.0$, corresponding to
the actual matter density profile such as given by the experiment
 definition file, and $\sigma_{\hat{\rho}}$ to the 
relative matter density uncertainty (\eg, $0.05$ for 5\% uncertainty).

@@

\index{norm}{External information!precision}
Eventually, a typical initialization of the external input with
$10\%$ external precisions for the solar 
parameters\footnote{In fact, accelerator-based long-baseline experiments 
are primarily sensitive to the product $\sin 2 \theta_{12} \cdot \sdm$, 
which means that these errors effectively add up to an error of this 
product of about $15\%$.}, 
and $5\%$ matter density uncertainties for all experiments looks like this:
\begin{quote}
{\tt
 glbDefineParams(input\_errors,theta12*0.1,0,0,0,sdm*0.1,0);\\  
 glbSetDensityParams(input\_errors,0.05,GLB\_ALL);\\
 glbSetCentralValues(true\_values);\\
 glbSetInputErrors(input\_errors);\\
}
\end{quote}
In this example, the central values are set to 
the true (simulated) values.

%JK - NO LONGER TRUE IN GLOBES 3.0
%Remember that initially the 
%matter density scaling factors are 
%all $1.0$, which means that they do not need to be adjusted for the
%central values.

@@

The projection onto the $\stheta$- (or $\deltacp$-) axis is performed by fixing $\stheta$ (or $\deltacp$) and minimizing the $\chi^2$-function over all free fit parameters and the matter densities. We illustrate this method by the example of the projection of the two-dimensional manifold in the $\stheta$-$\deltacp$-plane onto the $\stheta$-axis in \figu{projex}. In this figure, the left-hand plot shows the correlation in the $\stheta$-$\deltacp$-plane computed with {\tt glbChiSys}. The right-hand plot illustrates the projection of this two-dimensional manifold onto the $\stheta$ axis by minimizing $\chi^2$ over $\deltacp$. In this simple example, the minimization is done along the vertical gray lines in the left hand plot. The obtained minima are located on the thick gray curve, which means that the right-hand plot represents the $\chi^2$-value along this curve. In fact, one can easily see that one obtains the correct projected $3 \sigma$ errors in this example (\cf, arrows). This figure illustrates the projection of a two-parameter correlation. In general, the full $n$-parameter correlation is treated similarly by the simultaneous (local) minimization over all free fit parameters.

@@

\index{norm}{Matter density!scaling factor}
The output of the minimizer in {\tt out} carries as many matter density scaling factors as there are experiments. Either
one (for the simulation of one experiment) or all (for the simulation of
all experiments) are different from $1.0$ if matter density uncertainties
are present, since each experiment may face other matter density conditions. 
The minimizers of individual experiments ``know'' which
experiment they are currently treating, which means that they only return the
matter density scaling factor of the appropriate experiment.
For example, calculating {\tt glbChiTheta13} for the last experiment
number, the last density value will be returned.
This approach turns out to be extremely useful together with the
simulation of more than one experiment. One can, for instance, locate the
degeneracies of all individual experiments. In order to test if
these degeneracies are still present in the combination of all experiments (which has a very different topology), one can test the combination of experiments with the output {\tt out} from the individual experiments. In this case, even the correct matter density scaling factor
output is used.

@@

Since the number of different parameter vectors used by \GLOBES\ may be a bit confusing, we summarize the most common parameter sets used in the calculations:
\begin{description}
\item[The simulated/true values] are the values set in \GLB{SetRates}.
\item[The fit values] are the values in the first parameter {\tt in} of {\tt glbChiTheta13} (and the other minimization functions) which are {\em fixed} by definition (such as $\theta_{13}$ for {\tt glbChiTheta13}). 
\item[The starting point/educated guess for the minimizer] are the values in the first parameter {\tt in} of {\tt glbChiTheta13} (and the other minimization functions) which are {\em free} by definition (such as all but $\theta_{13}$ for {\tt glbChiTheta13}). 
\item[The minimization result] of the marginalization process are the values in the second parameter {\tt out} of {\tt glbChiTheta13} (and the other minimization functions) which are {\em free} by definition (such as all but $\theta_{13}$ for {\tt glbChiTheta13}). The other values in {\tt out} still correspond to the fit values. 
\item[The position of external priors,] \ie, the best-fit values of external input, is set by \GLB{SetCentralValues}.
\item[The magnitude of external errors,] \ie, the errors of external input, is set by \GLB{SetInputErrors}.
\end{description}

@@

In general, one can show the measurement result in any $k$-dimensional hyperplane, where $k$ is smaller than the dimension of the parameter space $n$, and thus the dimension of the fit manifold. In this case, $k$ parameters are fixed and $n-k$ parameters are minimized over. One such example is the projection of the fit manifold onto the $\stheta$-$\deltacp$-plane, \ie, $k=2$ here. In this case, the two
parameters $\stheta$ and $\deltacp$ are kept fixed, and the others are
minimized over. 
The corresponding function is 
\index{norm}{Projection!$\theta_{13}$-$\deltacp$-plane}
\begin{function}
\GLBNS{ChiTheta13Delta}
{\tt double glbChiTheta13Delta(const glb\_params in, glb\_params out, int exp)} returns the projected $\chi^2$ onto the $\theta_{13}$-$\deltacp$-plane for the  experiment {\tt exp}. For the simulation of all initialized experiments,
use {\tt GLB\_ALL} for {\tt exp}. The values in {\tt in} are the guessed fit values for the minimizer (all parameters other than $\theta_{13}$ and $\deltacp$) and the fixed fit values of $\theta_{13}$ and $\deltacp$. The actually determined parameters at the minimum are returned in {\tt out}, where $\theta_{13}$ and $\deltacp$ are still at their fixed values. If {\tt out} is set to {\tt NULL}, this information will not be returned.
\end{function}
This function works analogously to the ones in the last section. It can, for example, be used to obtain a figure similar to \figu{projex}, left.
The example on page~\pageref{ex:corrproj} illustrates then the difference
between the projections of the ``eggs'' within the 
$\stheta$-$\deltacp$-plane onto the $\theta_{13}$-axis. 
Though the running time for one call of these functions is somewhat 
shorter than the one for the $\stheta$- or $\deltacp$-projections, one 
has to compute a two-dimensional array for such a figure (instead of a 
one-dimensional list). Therefore, the overall computational effort is 
much higher, \ie, in the order of hours. In many cases, it is therefore
convenient to run {\tt glbChiSys} first to obtain a picture of
the manifold and to adjust the parameter ranges. Then, one can run
{\tt glbChiTheta13Delta} for a complete evaluation of the problem
including correlations.

@@

In order to define arbitrary projections, we introduce the vector
\GLB{\_projection}, which is very similar to the
oscillation parameter vector {\tt glb\_params}.
Normally, the user does not need to access this type directly:
A set of function similar to the ones for {\tt glb\_params} is
provided. The purpose of {\tt glb\_projection} is to tell \GLOBES\ 
which parameters are fixed, and which are minimized over. Thus, in
comparison to {\tt glb\_params}, it does not take values for the
parameters, but flags \GLBC{GLB\_FIXED} or \GLBC{GLB\_FREE}.
For example, the projection onto the $\theta_{13}$-axis {\tt glbChiTheta13}
is nothing else than a special case of {\tt glbChiNP} with $\theta_{13}$
fixed and all the other parameters free. Similar to {\tt glb\_params},
the type {\tt glb\_projection} has to be allocated first, and freed
later. The access functions for {\tt glb\_projection} are summarized in \Tab~\ref{tab:defprojection}. Since the complete set is very similar to
the one for {\tt glb\_params}, we do not go into greater details here.

@@

User-defined priors are an advanced concept of \GLOBES\ 3.0 and higher. Therefore,
this section can be skipped in a first reading of the manual.
They allow for arbitrary priors being added to the $\chi^2$ after the systematics
minimization and before the marginalization over the oscillation parameters (\cf, \equ{priors}).
Therefore, compared to user-defined systematics, they depend on the oscillation
parameters only, but not on the systematics parameters. Examples for applications
are non-Gaussian external input, the combination with externally simulated experiments, and the
constraint to certain parameter-subspaces (such as a specific octant).

@@

The prior function should expect the parameter structre {\tt glb\_params} containing the
current fit values and the {\tt void}-pointer {\tt user\_data} as arguments.
We show an example for a user-defined prior on page~\pageref{ex:userprior}. This prior
is simply registered with
\begin{quote}
{\tt
 glbInit(argv[0]); \\
 glbRegisterPriorFunction(my\_prior,NULL,NULL,NULL);
}
\end{quote}
and replaces the standard prior of \GLOBES . It behaves exactly as the standard prior, but
the solar mixing angle is interpreted as $\sin^2 \theta_{12}$ instead of $\theta_{12}$. Therefore,
a Gaussian error is imposed on $\sin^2 \theta_{12}$ instead of $\theta_{12}$, and the central
values and input errors are interpreted in terms of $\sin^2 \theta_{12}$ as well. Note that
one does not need to know if the prior was called for one experiment only or all experiments,
since this information is implicitely given by the different density projection flags being set
accordingly.
